% !TEX program = xelatex

\documentclass{resume}

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Patryk Targosiński}

\basicInfo{
  \email{patryk.targosinski@gmail.com} \textperiodcentered\ 
  \phone{(+48) 726 286 295} \textperiodcentered\ 
  \linkedin[tpatryk]{https://www.linkedin.com/in/tpatryk/}}

%\section{\faGraduationCap\ Education}
%\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{2013 -- Present}
%\textit{Master student} in Electronics Engineering (EE), expected March 2016
%\datedsubsection{\textbf{Xidian University}, Shaanxi, China}{2009 -- 2013}
%\textit{B.S.} in Electronics Engineering (EE)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Boombit} Warsaw, Poland}{Jul. 2023 -- Present}
\role{SDK Developer}{Core SDK Team}
I was part of the Core SDK team responsible for a set of libraries used in hundreds of games, generating over 50 million USD in annual revenue for the company.
Main highlights of my work:
\begin{itemize}
    \item Designed and developed a Unity SDK for a cross-promotion ad network.
    \item Redesigned and developed an enhanced Unity package to manage the downloading, caching, and loading of textures and asset bundles.
    \item Developed a Unity module to implement modern, native iOS and Android haptic feedback functionality.
\end{itemize}

\datedsubsection{\textbf{Huuuge Games}}{Feb. 2022 -- Jun. 2023}
\role{Unity Developer}{Huuuge Unity Framework SDK Team}
I was a part of Huuuge Unity Framework SDK Team. This SDK was used in publishing games and Traffic Puzzle game that has 10+ milion downloads worldwide.
My main contributions:
\begin{itemize}
  \item Implemented xxx feature
  \item Optimized xxx 5\%
  \item xxx
\end{itemize}

\datedsubsection{\textbf{Strangelet Studio}}{Jan. 2020 -- Jan. 2022}
\role{Unity Developer}{}
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

\datedsubsection{\textbf{Pixelated Milk}}{Dec. 2018 -- Dec. 2019}
\role{Unity Developer}{}
An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
\begin{itemize}
  \item Easy to be further customized or extended
  \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
  \item FontAwesome 4.5.0 support
\end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C#, Swift, Objective-C, Kotlin, Java, C++
  \item Development: iOS, Android, WebGL, Telegram
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
\datedline{Other awards}{2015}

%\section{\faInfo\ Miscellaneous}
%\begin{itemize}[parsep=0.5ex]
%  \item Blog: http://your.blog.me
%  \item GitHub: https://github.com/username
%  \item Languages: English - Fluent, Mandarin - Native speaker
%\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
